### 2018-05-16 Paper/examples.tex
..

>>>>

From the above figure, it can be said that the Sobol sensitivity indices are in excellent
agreement with the screening metric estimates. Consequently, the parameter ranks are
found to be consistent in the two plots. It is observed that the limit state function is
predominantly sensitive towards three parameters: $r$, $F$, and $t_1$. Hence, it seems
likely that an ROS in three dimensions is able to capture the uncertainty
in $g(\bm{X})$ due to uncertainty in the six parameters. To illustrate computational gains
as a result of dimension-reduction, we construct PCEs in 3D, 4D (accounts for the uncertainty
in $k_1$ as well), and the original 6D parameter domain. In Figure~\ref{fig:conv_osc}~(left), we
compare the rate of convergence of the PCEs. As expected, the third-order PCE converges much faster
than the other two. Consequently, the number of model evaluations required for a converged
PCE is expected to be relatively much smaller in this case.

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.48\textwidth]{./Figures/err_samples_oscillator}
  \includegraphics[width=0.48\textwidth]{./Figures/pdf_comp_oscillator}
\caption{Left: Logarithm of $\epsilon_{\mbox{\tiny{LOO}}}$ is against sample size for 
PCEs constructed in 3, 5, and 6 dimensions to compare their convergence characteristics. 
Right: PDF of the limit state function is plotted using the actual function in~\eqref{eq:limit}
and the third-order PCE.}
\label{fig:conv_osc}
\end{center}
\end{figure}
